BACI of biomass change for VOCC source cells for all years

### 2019-08-27 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
split BACI code to run separately by maturity class

@@

#### Set species
```{r echo=TRUE}
# # Species run so far...
# species <- "Arrowtooth Flounder"
 species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

params <- readRDS(paste0("data/optimal-values-by-species.rds"))
params <- params[rev(order(as.Date(params$date))), ]
params <- params[!duplicated(params$species), ]

optimal_do <- round(params[params$species == species, ]$optimal_do, digits = 2)
optimal_temp <- round(params[params$species == species, ]$optimal_temp, digits = 2)

optimal_values <- c(optimal_do, optimal_temp)
```

@@

Run all subsequent code...
```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
# library(gfdata)
library(sdmTMB)
#library(itsadug)
library(gfranges)
```

@@

if (climate == "temperature") {
  variable_names <- c("temp")
  min_thresholds <- c(Inf)
  #delta_threshold <- temp_threshold
  optimal_values <- optimal_temp
  max_thresholds <- temp_threshold
  indices <- c(1, 2)
  delta_t_total <- 2
  }

if (climate == "do") {
  variable_names <- c("do_est")
  max_thresholds <- c(Inf)
  #delta_threshold <- -1 * (do_threshold)
  optimal_values <- optimal_do
  min_thresholds <- do_threshold
  indices <- c(1, 2)
  delta_t_total <- 2
  }

@@

```{r}
rm(vocc)
#start_time <- NULL
vocc_by_year <- lapply(start_years, function(start_time) {

@@

all_vectors <- do.call("rbind", trimmed_vectors)

# if (length(vectors[, 2]) == 0) {
#   other_coefs <- readRDS(paste0("data/", climate_string, "-vocc-by-spp-sdmTMB-coefs.RDS"))
#   coefs <- other_coefs[1, ]
#   coefs$var <- "NA"
#   coefs$beta <- "NA"
#   coefs$se <- "NA"
#   coefs$model <- "NA"
#   coefs$species <- spp
#   coefs$lifestage <- "NA"
#   coefs$climate <- climate
#   coefs$min_thresholds <- min_string
#   coefs$max_thresholds <- max_string
#   coefs$optimum <- optimal_string
#   coefs$start_time <- start_time
#   coefs$timespan <- delta_t_total
#   coefs$region <- region
#   coefs$ssid_string <- ssid_string
# 
#   coefs <- rbind(other_coefs, coefs) %>% distinct()
#   saveRDS(coefs, file = paste0("data/", climate_string, "-vocc-by-spp-sdmTMB-coefs.RDS"))
# 
#   stop("No vectors. Conditions saved to 'data/vocc-byspp-sdmTMB-coefs'.")
# }
# glimpse(vocc)
# glimpse(vectors)
```

@@

  vocc_plot <- gridExtra::grid.arrange(
    vocc_plot_temp, vocc_plot_do,
    ncol = 2,
    top = grid::textGrob(paste("DO of ", optimal_values[1], "less", min_thresholds[1], "or temperature of ", optimal_values[2], "plus", max_thresholds[2], " over ", start_time, "-", start_time + delta_t_total, ""))
  )
}

vocc_plot
})

})

@@

Get all biomass predictions 
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=F}
priors <- FALSE
# priors <- TRUE

covariates <- "+muddy+any_rock"

covs <- gsub("\\+", "-", covariates)

rm(adult_predictions)
rm(imm_predictions)
rm(predictions)

try({
  adult_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-mat-biomass-prior-", priors, ".rds"
  ))
})

try({
  imm_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-imm-biomass-prior-", priors, ".rds"
  ))
})

try({
  predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-total-biomass-prior-", priors, ".rds"
  ))
})

if (!exists("adult_predictions")) adult_predictions <- NULL
if (!exists("imm_predictions")) imm_predictions <- NULL
if (!exists("predictions")) predictions <- NULL

biomass_list <- list(
  adult = adult_predictions,
  imm = imm_predictions,
  total = predictions
)

biomass_list <- biomass_list[!sapply(biomass_list, is.null)]
# glimpse(biomass_list)
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}
alldata <- lapply(biomass_list, function(split_bio_data) {

@@

   biomass_by_year[[j]] <- make_trend_data(split_bio_data,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
  }

@@

  biomass_covs <- split_bio_data %>% 
    select(X, Y, depth, trawled, muddy, any_rock, omega_s) %>% 
    distinct()

@@

  # keep just one row for each cell that exceeded the end climate threshold 
  source_cells <- all_vectors %>% filter (distance > (- dist_intercept)) %>% 
    distinct(icell, start_time, .keep_all = TRUE) %>% 
    select(-target_X, -target_Y, -target_values, -tid)

@@

  # identify all possible control cells have been given a distance == - dist_intercept

  control_cells <- all_vectors %>% filter (distance == (- dist_intercept)) %>% 
    distinct(icell, start_time, .keep_all = TRUE) %>% 
    mutate(distance = (- dist_intercept)) %>% 
    select(-target_X, -target_Y, -target_values, -tid)

@@

  alldata
})
```

```{r, include=FALSE, echo=FALSE}
lapply(alldata, function(i){ggplot(i, aes(x=cell_type, y=log(start_density))) + geom_boxplot()+facet_wrap(~start_time)})
```

# Select matched control cells
```{r}
matched <- lapply(alldata, function(alldata) {  
  ## trim non-overlapping values to reduce size of dataset 
  control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat=="1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

@@

  # need to be standardized? seems not
  alldata$depth2 <- alldata$depth^2
  alldata$start_density.st <- round(arm::rescale(log(alldata$start_density))*5)/5
  alldata$start_density_st <- round(arm::rescale(log(alldata$start_density)), 1)
  alldata$depth.st <- arm::rescale(log(alldata$depth)) 
  alldata$muddy.st <- arm::rescale(alldata$muddy) 
  alldata$any_rock.st <- arm::rescale(alldata$any_rock) 
  #alldata$omega_s.st <- arm::rescale(alldata$omega_s)

 ## Using optimization ... doesn't work   
  # if(
  #   class(
  #   try(
  #     fit_formula <- paste0("treat ~ start_density_st + depth.st + muddy.st + any_rock.st") 
  #   # fit_formula <- paste0("treat ~ start_density_st") 
  #   # fit_formula <- paste0("treat ~ start_density_st + depth.st") 
  #   # # for (j in (variable_names)) {
  #   # #   fit_formula <- paste0("", fit_formula, " + ", j, "_s")
  #   # #   }
  #     # options("optmatch_max_problem_size" = Inf)
  #     matched <- MatchIt::matchit(as.formula(fit_formula), method = "optimal", data = alldata)
  #     , silent = TRUE)
  #     ) == "try-error"){

  # Using exact match and rounding
  fit_formula <- paste0("treat ~ depth.st + muddy.st + any_rock.st + 
    trawled + omega_s + x + y") #
  # for (j in (variable_names)) {
  #   fit_formula <- paste0("", fit_formula, " + ", j, "_s")
  #   }

  # Choose data order
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]

  matched <- MatchIt::matchit(as.formula(fit_formula), 
    exact = c("start_density.st", "start_time"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard="control",
    data = alldata)

  #}

  #matched

})
```

Print diagnostics for matching
```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
lapply(matched, function(i){  
  summary(i)
  plot(i)
  })
```

Prep matched data for analysis
```{r}
vocc_by_sp <- lapply(matched, function(matched) {    
  mdata <- MatchIt::match.data(matched, distance = "pscore")

@@

  # if selecting 2 matches
  # controls2 <- mdata[matched$match.matrix, ]
  # controls2$origobs <- row.names(controls)   
  # controls2$matchobs <- matched$match.matrix[,2]

@@

  # rename spatial coordinates for inclusion in models and plots without naming conflicts
  data <- vocc_by_sp %>%
    rename(X = x, Y = y)
      #%>% rename(distance = vect_dist) %>% select(-start_density.st, -depth.st, -muddy.st, -any_rock.st, -omega_s.st)
  # other variable prep
  data$log_density <-  log(data$density)
  data$vect_dist2 <- data$vect_dist^2
  data <- mutate(data, time = ifelse(after==1, "end", "begin"))
  data$matchobs <- as.factor(data$matchobs)
  data$origobs  <- as.factor(data$origobs)   
  data$start_time <- as.factor(data$start_time)

  data

})
```

## Adults
```{r}
data <- vocc_by_sp [["adult"]]
# View(data)
```

### Plot matches
```{r}
ggplot(data, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=as.factor(matchobs))) +
  geom_point(alpha=0.8, size = 1.5) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()

lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") +
  theme_bw()
})

ggplot(data, aes(y=log_density, x=depth, colour=cell_type)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") +
  facet_wrap(~time) +
  theme_bw()

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)+
  theme_bw()

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.45) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)+
  theme_bw()

@@

ggplot(data, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = dat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(start_time~time)+
  theme_bw()
```

### Basic BACI
```{r}
#FIXME: need to nest random effects

for (j in (variable_names)) {
  baci_formula <- paste0("log_density~after + cell_type + after:cell_type + n_targets + vect_dist + vect_dist2 + std_", j, "+ std_", j, "2 + (1|icell) + (1|matchobs) + (1|start_time)")
}

@@

### GAMM
```{r}
for (j in (variable_names)) {
  gamm_formula <- paste0("log_density ~ time * cell_type + s(vect_dist) + s(std_", j, ") + s(X,Y)")
}

gam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs) + (1|start_time), data=data) # + s(X,Y, bs="re")

summary(gam4$gam) ## summary of gam

@@

```{r,  results="hide", include=FALSE}
plot_parametric(gam4$gam, pred=list(time=c("begin","end"), cell_type=c("control", "source")), parametricOnly = TRUE, main="", xlab ="log_density"
  #, groups = cell_type, gcolor = my_cols, color = my_cols["time"]
  ) 
```

@@

### Plot matches
```{r}
ggplot(idata, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=matchobs)) +
  geom_point(alpha=0.4, size = 2) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()

lapply(variable_names, function(j) {
ggplot(idata, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") 
})
ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~time)

idat_summary <- idata %>% 
  group_by(start_time, cell_type) %>% 
  tally() %>% filter(cell_type=="source")

ggplot(idata, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = idat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(start_time~time)+
  theme_bw()
```

### Basic BACI
```{r}

mi <- lmerTest::lmer(as.formula(baci_formula), data=idata)
summary(mi)
```

@@

### GAMM
```{r}
# for (j in (variable_names)) {
#   gamm_formula <- paste0("log_density ~ time * cell_type + s(vect_dist) + s(std_", j, ") + s(X,Y)")
# }

#FIXME: need to nest random effects

igam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs) + (1|start_time), data=idata) # + s(X,Y, bs="re")

summary(igam4$gam) ## summary of gam

>>>>

Should optimal temperature vary for age classes? Seems likely. 
Therefore need separate VOCC trimming and matching for age classes -> change function structure to choose age upfront

Should matches be selected based on exact depth categories in addition to density (all within time periods)?
What does it mean for the analysis that the depth range at which VOCC occur within a species temperature range varies dramatically between time periods?

@@

#### Set species
```{r echo=TRUE}
# # Species run so far...
 species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

#### Set age class
```{r echo=TRUE}
age <- "mature" # or mostly so
# age <- "imm"
```

@@

Run all subsequent code...
```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
# library(gfdata)
library(sdmTMB)
# library(itsadug)
library(gfranges)
```

params <- readRDS(paste0("data/optimal-values-by-species-by-age.rds"))

if (age == "imm") {
  params <- filter(params, age == "imm")
} else {
  params <- filter(params, age != "imm")
}
params <- params[rev(order(params$maxy)), ]
params <- params[!duplicated(params$species), ]

#optimal_do <- round(params[params$species == species, ]$optimal_do, digits = 2)
optimal_temp <- round(params[params$species == species, ]$optimal_temp, digits = 2)

#optimal_values <- c(optimal_do, optimal_temp)
```

@@

if (climate == "temperature") {
  variable_names <- c("temp")
  min_thresholds <- c(Inf)
  optimal_values <- optimal_temp
  max_thresholds <- temp_threshold
  indices <- c(1, 2)
  delta_t_total <- 2
  }

if (climate == "do") {
  variable_names <- c("do_est")
  max_thresholds <- c(Inf)
  optimal_values <- optimal_do
  min_thresholds <- do_threshold
  indices <- c(1, 2)
  delta_t_total <- 2
  }

@@

```{r}
rm(vocc)

vocc_by_year <- lapply(start_years, function(start_time) {

@@

all_vectors <- do.call("rbind", trimmed_vectors)
```

@@

  vocc_plot <- gridExtra::grid.arrange(
    vocc_plot_temp, vocc_plot_do,
    ncol = 2,
    top = grid::textGrob(paste(
      "DO of ", optimal_values[1], "less", min_thresholds[1], 
      "or temperature of ", optimal_values[2], "plus", max_thresholds[2], 
      " over ", start_time, "-", start_time + delta_t_total, ""))
  )
}
vocc_plot
})
})

@@

Get all biomass predictions 
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=F}
priors <- FALSE
covariates <- "+muddy+any_rock"
covs <- gsub("\\+", "-", covariates)

rm(biomass_predictions)

if (age == "imm") {
  try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-imm-biomass-prior-", priors, ".rds"
  ))
})
} else {
try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-mat-biomass-prior-", priors, ".rds"
  ))
})
if (!exists("biomass_predictions")) {
try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-total-biomass-prior-", priors, ".rds"
  ))
})
}
}
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}
#alldata <- lapply(biomass_list, function(biomass_predictions) {

@@

   biomass_by_year[[j]] <- make_trend_data(biomass_predictions,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
  }

@@

  biomass_covs <- biomass_predictions %>% 
    select(X, Y, depth, trawled, muddy, any_rock, omega_s) %>% 
    distinct()

@@

  # keep just one row for each cell that exceeded the end climate threshold 
  source_cells <- all_vectors %>% filter(distance > (-dist_intercept)) %>% 
    distinct(icell, start_time, .keep_all = TRUE) %>% 
    select(-target_X, -target_Y, -target_values, -tid)

@@

  # identify all possible control cells have been given a distance == - dist_intercept
  control_cells <- all_vectors %>% filter(distance == (-dist_intercept)) %>% 
    distinct(icell, start_time, .keep_all = TRUE) %>% 
    mutate(distance = (- dist_intercept)) %>% 
    select(-target_X, -target_Y, -target_values, -tid)

@@

  alldata
#})
```

```{r eval=FALSE, include=FALSE, echo=FALSE}
# lapply(alldata, function(i){ggplot(i, aes(x=cell_type, y=log(start_density))) + geom_boxplot()+facet_wrap(~start_time)})
```

# Select matched control cells
```{r}
rm(vocc_by_sp)
try({
  vocc_by_sp <- readRDS(paste0(
    "data/ BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-multiyear-all.rds"
  ))
})

match_formula <- paste0("treat ~ 
  muddy.st + any_rock.st + x + y") #depth.st + trawled + omega_s + 
  # for (j in (variable_names)) {
  #   fit_formula <- paste0("", fit_formula, " + ", j, "_s")
  #   }

if (!exists("vocc_by_sp")){
# matched <- lapply(alldata, function(alldata) {

  ## trim non-overlapping values to reduce size of dataset 
  control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat=="1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

@@

  # need to be standardized? seems not
  alldata$depth2 <- alldata$depth^2
  alldata$start_density.st <- round(arm::rescale(log(alldata$start_density))*5)/5
  alldata$depth.st <- round(arm::rescale(log(alldata$depth))*5)/5
  alldata$muddy.st <- arm::rescale(alldata$muddy) 
  alldata$any_rock.st <- arm::rescale(alldata$any_rock) 
  #alldata$omega_s.st <- arm::rescale(alldata$omega_s)

 ## Using optimization ... doesn't work   
  # alldata$start_density_st <- round(arm::rescale(log(alldata$start_density)), 1)
  # fit_formula <- 
  #   paste0("treat ~ start_density_st + depth.st + muddy.st + any_rock.st") 
  # # for (j in (variable_names)) {
  # #   fit_formula <- paste0("", fit_formula, " + ", j, "_s")
  # #   }
  # # options("optmatch_max_problem_size" = Inf)
  # matched <- MatchIt::matchit(as.formula(fit_formula), 
  #     method = "optimal", data = alldata)

  # # Using exact match and rounding
  # # Choose data order if not using random
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]

  matched <- MatchIt::matchit(as.formula(match_formula), 
    exact = c("start_density.st", "start_time", "depth.st"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard="both",
    data = alldata)
  # matched
# })
}
```

Print diagnostics for matching
```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
if (!exists("vocc_by_sp")){
match_plots <- lapply(matched, function(i){  
  summary(i)
  plot(i)
  })
match_plots
}
```

Prep matched data for analysis
```{r}
if (!exists("vocc_by_sp")){
#vocc_by_sp <- lapply(matched, function(matched) {    
  mdata <- MatchIt::match.data(matched, distance = "pscore")

@@

@@

  # rename spatial coordinates to avoid naming conflict with y~x notation
  data <- vocc_by_sp %>%
    rename(X = x, Y = y)
    # %>% rename(distance = vect_dist) %>% 
    # select(-start_density.st, -depth.st, -muddy.st, -any_rock.st, -omega_s.st)

  # other variable prep
  data$log_density <-  log(data$density)
  data$log_depth <-  log(data$depth)
  data$std_log_depth <- arm::rescale(log(data$depth))
  data$vect_dist2 <- data$vect_dist^2
  data <- mutate(data, time = ifelse(after==1, "end", "begin"))
  data$matchobs <- as.factor(data$matchobs)
  data$origobs  <- as.factor(data$origobs)   
  data$start_time <- as.factor(data$start_time)

#  data
#})
vocc_by_sp <- list()
vocc_by_sp[[1]] <- data
vocc_by_sp[[3]] <- match_formula  
vocc_by_sp[[4]] <- match_plots
saveRDS(vocc_by_sp, file = paste0(
    "data/ BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-multiyear-all.rds"
  ))
}
```

## Adults
```{r}
try({
  vocc_by_sp <- readRDS(paste0(
    "data/ BACI-", species, "-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-multiyear-all.rds"
  ))
})
data <- vocc_by_sp [["adult"]]
# View(data)
```

### Plot matches
```{r}
dat_summary <- data %>% 
  group_by(start_time, cell_type) %>%
  tally() %>% filter(cell_type=="source")
data_depth <- data %>% 
  group_by(start_time) %>% 
  mutate(mean_depth = mean(depth))

ggplot(data, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=as.factor(matchobs))) +
  geom_point(alpha=0.8, size = 1) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()

lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") +
  facet_grid(start_time~cell_type) +
  theme_bw()
})

ggplot(data, aes(std_log_depth, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~start_time) +
  theme_bw()
#  
# ggplot(data, aes(y=log_density, x=depth, colour=cell_type)) +
#   geom_point(alpha=0.35) +
#   scale_colour_viridis_d(option="C") +
#     facet_grid(start_time~time) +
#   theme_bw()

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_grid(start_time~time, scales = 'fixed') +
  theme_bw()

ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.45) +
  scale_fill_viridis_d(option="C") +
  facet_grid(time~start_time) +
  theme_bw()

@@

ggplot(data, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = dat_summary,
            aes(cell_type, max(data$log_density)-1, label = n), hjust = -0.3) +
  facet_grid(time~start_time) +
  theme_bw()
```

### Basic BACI
```{r}
for (j in (variable_names)) {
  baci_formula <- paste0("log_density~after + cell_type + after:cell_type + n_targets + vect_dist + vect_dist2 + std_", j, "+ std_", j, "2 + (1|icell) + (1|matchobs) + (1|start_time)")
}

@@

### GAMM
```{r}
 gamm_formula <- paste0("log_density ~ ", 
  # "time * start_time + ",
  #"start_time * cell_type + ",
  "time * cell_type + s(vect_dist) + s(std_log_depth) + s(X,Y)")

for (j in (variable_names)) {
 gamm_formula <- paste0(gamm_formula, "+ s(std_", j, ")")
 }

gam4 <- gamm4::gamm4(as.formula(gamm_formula), 
  random = ~(1|matchobs) + (1|icell) 
   + (1|start_time)
  # + (time|start_time) 
  # + (cell_type|start_time)
  , data=data)

summary(gam4$gam)

@@

```{r,  results="hide", include=FALSE}
plot_parametric(gam4$gam, pred=list(time=c("begin","end"), cell_type=c("control", "source"), start_time=c("2009","2011","2013","2015")), parametricOnly = TRUE, main="", xlab ="log_density"
  #, groups = cell_type, gcolor = my_cols, color = my_cols["time"]
  ) 
```

@@

### Plot matches
```{r}
idat_summary <- idata %>% 
  group_by(start_time, cell_type) %>%
  tally() %>% filter(cell_type=="source")
idata_depth <- idata %>% 
  group_by(start_time) %>% 
  mutate(mean_depth = mean(depth))

ggplot(idata, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=matchobs)) +
  geom_point(alpha=0.4, size = 1) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()

lapply(variable_names, function(j) {
ggplot(idata, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C")+
  facet_grid(start_time~cell_type) +
  theme_bw() 
})

# ggplot(data, aes(y=log_density, x=depth, colour=cell_type)) +
#   geom_point(alpha=0.35) +
#   scale_colour_viridis_d(option="C") +
#     facet_grid(start_time~time) +
#   geom_text(data = idata_depth,
#     aes(150, 0.5, label = round(mean_depth)), hjust = -0.3, inherit.aes = FALSE) +
#   theme_bw()
ggplot(idata, aes(depth, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~start_time) +
  theme_bw()

ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_grid(start_time~time) +
  geom_text(data = idat_summary,
            aes(1, 0.75, label = n), hjust = -0.3) +
  theme_bw()

ggplot(idata, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_grid(time~start_time) +
  theme_bw()

ggplot(idata, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = idat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(time~start_time) +
  theme_bw()
```

### Basic BACI
```{r}
mi <- lmerTest::lmer(as.formula(baci_formula), data=idata)
summary(mi)
```

@@

### GAMM
```{r}
# for (j in (variable_names)) {
#  gamm_formula <- paste0("log_density ~ ", 
#   # "time * start_time + ",
#   "start_time * cell_type + ",
#   "time * cell_type + s(vect_dist) + s(std_", j, ") + s(X,Y)")
#  }
igam4 <- gamm4::gamm4(as.formula(gamm_formula), 
  random = ~(1|matchobs) + (1|icell) 
   + (1|start_time)
  # + (time|start_time) 
  # + (cell_type|start_time)
  , data=idata)

summary(igam4$gam)
